\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-11 paper/main.tex
Added selection criterion

\Fix{Abid, explain the rationale for selecting jax, torch, and tf.}

\Fix{Abid, explain the criterion for selecting the bugs (e.g., it
  contains test code showing the problem).}

>>>>

% \Fix{Abid, explain the rationale for selecting jax, torch, and tf.}

Amongst many DL libraries, the most popular libraries for developing AI-enabled applications and used in testing tools are \torch~and \tf. \jax~is a relatively newer entry to the list of libraries but it is rapidly gaining popularity as well. All three of these libraries are open source with active communities that support the libraries, making them very suitable for developing testing tools around. We chose these three popular datasets in order to enhance the process of developing testing tools around these libraries.

% \Fix{Abid, explain the criterion for selecting the bugs (e.g., it
  % contains test code showing the problem).}

For the bugs from these libraries, we focused on bug reports that have been accepted by the developer community as true bugs. We determine this by checking whether the bugs have appropriate labels and have been fixed with pull requests linked to them. Among these confirmed bug reports, we choose the ones that have enough information to reproduce the bugs i.e. code to reproduce the bug, enviroment required for reproduction, clear description of desired behavior etc. Once we can successfully reproduce the bug by creating the enviroment detailed in the report, we choose the bug to be included in our dataset.

\Fix{Please review and revise}
